### 2023-08-10 thesis/sections/2-background.tex
thesis

\section{Background and Related Work}
\label{sec:background}
% subsections are \subsection{title}
%% subssubsections are \subsubsection{title}
%% numbering will work automatically

@@

\subsection{Dataset}
\cmtDK[inline]{\\
    - CLEVR \\
    ---- 3D objects \\
    ---- simple objects
}
\subsection{Language Games}
\cmtDK[inline]{\\
    - EGG \\
    - Resnet \\
    - CLEVR baselines \\
}

>>>>

\section{Background and Related Work}
\label{sec:background}

@@

\subsection{Language Games}
% \begin{itemize}
%     \item why language games?
%           \begin{itemize}
%               \item origins of language
%               \item flexibility
%               \item efficiency
%           \end{itemize}
%     \item setup of language game
%           \begin{itemize}
%               \item cooperative vs self-interested
%               \item asymetry
%               \item gumbel softmax vs reinforce
%               \item EGG
%               \item bottleneck
%           \end{itemize}
%     \item how does emerged language look?
%           \begin{itemize}
%               \item compositionality
%               \item generalization
%               \item efficiency
%               \item referring expressions
%               \item discriminative vs description
%               \item entropy minimization
%           \end{itemize}
%     \item why relating objects?
% \end{itemize}

The center of this thesis evolves around language games between deep neural models.
Hereby, multiple deep neural agents need to solve a task, by communicating with symbols, which initially are not associated with any meaning.
By using and interpreting these symbols in there communication, the agents start to give these symbols and their combinations meaning.
After this process, a new artificial language emerged, with which the agents can communicate with each other.

In section \ref{sec:aims_languages}, I will explain reasons, why research in this field is conducted and how it may help in further research.
Section \ref{sec:setup-lg} shows in more detail, how the language games are set up and how exactly agents can communicate and the language emerges.
In section \ref{sec:properties-el}, I will discuss, how the emerged languages can be built up.
Finally, section \ref{sec:referring} discusses, how the language games will be used in this thesis, to explore how agents can refer to objects in images.

\subsubsection{Aims of emerged languages}
\label{sec:aims_languages}
The setup of language games allows for very controlled rules of how agents can behave.

\subsubsection{Setup of language games}
\label{sec:setup-lg}
The term of 'language games' was first introduced by \citet{Wittgenstein1953}.
The author describes language games as uses of language between multiple interlocutors.
These can be any small parts of conversations, for instance between a teacher and a student teaching a new concept or between two persons, discussing a topic.
The rules in each of these situations differ and therefore the meanings and semantics of words and sentences may differ from situation to situation.
An interjection 'Water!' may be a warning, an answer to a question, a request or something else, depending on the context.
The meanings are bound to the rules of the language games.

This reasoning was taken up, when trying to train artificial entities to produce a language.
One of the original games is the signaling game, proposed by \citet{Lewis1969}.
In this game, a sender needs to send a message to a receiver, based on information only available to the sender.
Based on the message, the receiver proposes an action.
Both sender and receiver are rewarded in the same way if the proposed action was correct.
Hence, both agents need to invent a language together, fit to the conditions of the game.

The entities can be set into real or simulated interactive situation, a language game, that meaning and a language can emerge (\citet{Kirby2002}).
Multiple deep neural models, called agents, communicate with a set of symbols to solve a task.
Guided by the task and the rules, how agents can generate and interpret symbols, a language can emerge.

% This reasoning was taken up, when trying to train deep neural models to produce language.
% These models need to be set into an interactive situation, a language game, that meaning and a language can emerge (\citet{Baroni2020}).
% Multiple deep neural models, called agents, communicate with a set of symbols to solve a task.
% Guided by the task and the rules, how agents can generate and interpret symbols, a language can emerge.

\subsubsection{Properties of the emerged language}
\label{sec:properties-el}

\subsubsection{Referring to objects and grounding}
\label{sec:referring}

\subsection{Dataset}
\cmtDK[inline]{\\
    - CLEVR \\
    ---- 3D objects \\
    ---- simple objects \\
    - CLEVR baselines \\
}

\subsection{Computational methods}

### 2023-08-10 thesis/sections/3-exp-setup.tex
fix callback
thesis

\begin{figure}[h]
    \centering
    \subfigure['CLEVR single', \emph{large yellow sphere}]{
        \includegraphics[width=0.42\linewidth]{figures/CLEVR_single.png}
        \label{fig:clevr-single}
    }
    \subfigure['CLEVR unambiguous', \emph{large green sphere}]{
        \includegraphics[width=0.42\linewidth]{figures/CLEVR_unambiguous.png}
        \label{fig:clevr-unambiguous}
    }
    \subfigure['CLEVR color', \emph{small brown cylinder}]{
        \includegraphics[width=0.42\linewidth]{figures/CLEVR_color.png}
        \label{fig:clevr-color}
    }
    \subfigure['Dale-2', \emph{small green cylinder}]{
        \includegraphics[width=0.42\linewidth]{figures/CLEVR_dale-2.png}
        \label{fig:clevr-dale-2}
    }
    \subfigure['Dale-5', \emph{large purple cylinder}]{
        \includegraphics[width=0.42\linewidth]{figures/CLEVR_dale-5.png}
        \label{fig:clevr-dale-5}
    }
    \caption{Example images of each dataset, with the target object specified}
    \label{fig:clevr-examples}
\end{figure}

@@

\subsubsection*{CLEVR unambiguous}
The second dataset that is created is called 'CLEVR unambiguous'.
The purpose of this dataset is to create scenes, where the target object is completely unique and as easily identifiable as possible.
For this reason, there exist only two groups in the scene, the target object and distractors.
The distractor group can contain in between 6 and 9 objects.
The target object doesn't share any attributes with the distractors.
Namely, if the target is for instance green, no other object in the scene is green as well.
This also applies to the other attributes.
When referring to this target object, it is therefore enough to only describe one of the attributes.

Consider the scene in Figure \ref{fig:clevr-unambiguous}.
The target object can be completely described as the \emph{large green sphere}.
On the other hand, also descriptions like the \emph{green object}, the \emph{large object} or the \emph{sphere} would be unambiguously referring to the target object.

@@

The bounding box classifier is trained on all datasets excluding the 'CLEVR single'.
The 'CLEVR unambiguous' and 'CLEVR color' datasets are directly comparable to each other for the similar setup of their creation.
Especially interesting is the effect of the number of shared attributes. Does it help the model if the target object is unique in every attribute or does it help if there is only one specific attribute that is shared?
A similar assumption can be made for the 'Dale' datasets. How big is the effect of increasing the number of distractors and the growing number of attributes that are needed to discriminate the objects.

@@

For the sender, the images are passed through a feature extractor and a following linear layer that reduces the dimensions to an embedding size $e_s$.
All embedded images are concatenated and passed through another linear layer to reduce the dimensions to the hidden size $h_s$.
This is then used as the initial state of the encoder LSTM in the sender wrapper.

@@

During the experiments, the effects of the following variables are compared:
(1) the vocabulary size $|V|$,
(2) the LSTM hidden size of the sender wrapper $h_s$,
(3) the LSTM hidden size of the receiver wrapper $h_r$ and
(4) the embedding size of the sender $e_s$.

>>>>

\begin{figure}[h]
    \centering
    \subfigure['CLEVR single', \emph{large yellow sphere}]{
        \includegraphics[width=0.43\linewidth]{figures/CLEVR_single.png}
        \label{fig:clevr-single}
    }
    \subfigure['CLEVR color', \emph{small brown cylinder}]{
        \includegraphics[width=0.43\linewidth]{figures/CLEVR_color.png}
        \label{fig:clevr-color}
    }
    \subfigure['Dale-2', \emph{small green cylinder}]{
        \includegraphics[width=0.43\linewidth]{figures/CLEVR_dale-2.png}
        \label{fig:clevr-dale-2}
    }
    \subfigure['Dale-5', \emph{large purple cylinder}]{
        \includegraphics[width=0.43\linewidth]{figures/CLEVR_dale-5.png}
        \label{fig:clevr-dale-5}
    }
    \caption{Example images of each dataset, with the target object specified}
    \label{fig:clevr-examples}
\end{figure}

@@

@@

The bounding box classifier is trained on all datasets excluding the 'CLEVR single'.
The 'Dale' datasets are directly comparable to each other for the similar setup of their creation.
Especially interesting is the effect of the increasing the number of distractors and the growing number of attributes that are needed to discriminate the objects.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=.8\linewidth]{figures/discriminator.png}
    \caption{Sender and receiver architectures in the discrimination game}
    \label{fig:discriminator_architecture}
\end{figure}

Figure \ref{fig:discriminator_architecture} shows, how the sender and the receiver of the discriminator are built up.
For the sender, the images are passed through a feature extractor and a following linear layer that reduces the dimensions to an embedding size $e_s$.
All embedded images are concatenated and passed through another linear layer to reduce the dimensions to the hidden size $h_s$.
This is then used as the initial state of the encoder LSTM in the sender wrapper.

@@

During the experiments, the effects of the following variables are compared:
(1) the vocabulary size $|V|$,
(2) the LSTM hidden size of the sender wrapper $h_s$,
(3) the LSTM hidden size of the receiver wrapper $h_r$ and
(4) the embedding size of the sender $e_s$.
As before, the metrics to evaluate the results are the same as in the pre-experiments.

### 2023-08-10 thesis/sections/4-results.tex
thesis

When the target object \textbf{attributes are encoded as one-hot vectors} and added to the input, the results don't improve.
One factor that now has a much higher impact is the feature extractor that is used.
Table \ref{tab:feature-extractor-mean-distances} compares the mean distances the models predict for the different feature extractors.
The results are shown for the models trained on the Dale-2 and Dale-5 datasets for training and test data.
First, a big difference can be seen between the datasets.
The model doesn't converge on the correct coordinates for the Dale-5 dataset at all, looking at the test data.
All resulting mean distances are in a similar range around 50 pixels.
Using the Dale-2 dataset, the behavior is a little different.
All ResNet extractors with four residual blocks and optionally additional average pooling and classifier layers reach similar scores as the experiments before without any one-hot encodings.
Interestingly, using less residual layers, the model doesn't converge at all and the mean distances jump up and down between the epochs.
This effect also applies when using less residual blocks.
Using the VGG, both using VGG-avg and VGG-cls2 achieve a similar performance, while the others predict coordinates between 43 and 46 pixels away.
\cmtDK{compare to scratch}

\begin{table}[h]
    \centering
    \begin{tabular}{rcccc}
        \toprule
                            & \multicolumn{2}{c}{\textbf{Dale-2}} & \multicolumn{2}{c}{\textbf{Dale-5}}                                   \\\cmidrule(lr){2-3}\cmidrule(lr){4-5}
                            & train                               & test                                & train          & test           \\\midrule
        \textbf{VGG-0}      & 30,26                               & 46,2                                & \textbf{10,81} & 48,33          \\
        \textbf{VGG-avg}    & \textbf{9,96}                       & 36,9                                & 32,17          & 54,40          \\
        \textbf{VGG-cls1}   & 37,99                               & 43,28                               & 46,57          & 50,75          \\
        \textbf{VGG-cls2}   & 34,95                               & \textbf{36,32}                      & 47,63          & \textbf{46,38} \\
        \textbf{VGG-cls3}   & 39,99                               & 44,32                               & 47,26          & 46,77          \\\midrule
        \textbf{ResNet-3}   & 92,07                               & 91,12                               & 11,52          & 48,52          \\
        \textbf{ResNet-4}   & \textbf{8,09}                       & \textbf{36,78}                      & \textbf{9,05}  & 46,84          \\
        \textbf{ResNet-avg} & 29,21                               & 38,94                               & 37,10          & 48,71          \\
        \textbf{ResNet-cls} & 33,29                               & 38,83                               & 41,57          & \textbf{46,57} \\
        \bottomrule
    \end{tabular}
    \caption{Mean test losses for different feature extractors with one-hot attribute encodings after 20 epochs}
    \label{tab:feature-extractor-mean-distances}
\end{table}
\cmtDK{wrong numbers}
Secondly, the training loss now looks also different.
In almost no cases, the models converge to a very low mean distance, meaning a high precision in their predictions, as they did in the experiment before.
There are only exceptions when ResNet-4 is used or respectively VGG-avg for Dale-2 and VGG-0 for Dale-5.
In other words, that means that the models are again not able to generalize, but in specific cases to learn the patterns in the train data by heart.
This hints to the fact that only specific layers of the feature extractors contain information that is generally usable to identify and discriminate objects.
Especially high layers, like the classifier layers and in the case of ResNet also the average pooling layers seem to already encode to task specific knowledge that was learned during the pre-training of these deep neural models.
This information can't be utilized for the tasks in this research and earlier layers with more abstract information need to be used.
The experiments in the following sections are set up using these lower layers as ResNet-3, ResNet-4, VGG-0 and VGG-avg.

@@

In a next step, information about the attributes is included using the \emph{GRE-algorithm} from \citet{Dale1995}.
\cmtDK{change}

@@

These results allow two conclusions.
First, the models are biased to predict

Second, even though the models are biased towards the center of the image, the predictions are still often leaning in the direction of the target object.
This indicates that it is still able to

@@

Table \ref{tab:results} shows the accuracy of the models calculated on the success of communication if the receiver can identify the target object.
A random guess corresponds to 50\% in the \emph{Dale-2} dataset and 20\% in the \emph{Dale-5} dataset.

\begin{table}[h]
    \centering
    \begin{tabular}{ccccc|cc|cc|cc|cc}
        \toprule
              &         &         &         &         & \multicolumn{2}{c}{\textbf{Dale-2}} & \multicolumn{2}{c}{\textbf{Dale-4}} & \multicolumn{2}{c}{\textbf{CLEVR color}} & \multicolumn{2}{c}{\textbf{CLEVR unambiguous}}                                                                     \\\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-11}\cmidrule(lr){12-13}
        $|V|$ & $h_{s}$ & $h_{r}$ & $e_{s}$ & $e_{r}$ & \textbf{Acc.}                       & \textbf{length}                     & \textbf{Acc.}                            & \textbf{length}                                & \textbf{Acc.} & \textbf{length} & \textbf{Acc.} & \textbf{length} \\\midrule
        {10}  & {10}    & {10}    & {10}    & {10}    & {\%}                                & {}                                  & {\%}                                     & {}                                             & {\%}          & {}              & {\%}          & {}              \\
        {10}  & {10}    & {10}    & {50}    & {50}    & {\%}                                & {}                                  & {\%}                                     & {}                                             & {\%}          & {}              & {\%}          & {}              \\
        {13}  & {10}    & {10}    & {10}    & {10}    & {\%}                                & {}                                  & {\%}                                     & {}                                             & {\%}          & {}              & {\%}          & {}              \\
        {13}  & {10}    & {10}    & {50}    & {50}    & {\%}                                & {}                                  & {\%}                                     & {}                                             & {\%}          & {}              & {\%}          & {}              \\
        {20}  & {10}    & {10}    & {50}    & {50}    & {\%}                                & {}                                  & {\%}                                     & {}                                             & {\%}          & {}              & {\%}          & {}              \\
        {100} & {10}    & {10}    & {10}    & {10}    & {\%}                                & {}                                  & {\%}                                     & {}                                             & {\%}          & {}              & {\%}          & {}              \\
        {100} & {10}    & {10}    & {50}    & {50}    & {\%}                                & {}                                  & {\%}                                     & {}                                             & {\%}          & {}              & {\%}          & {}              \\
        {100} & {100}   & {100}   & {100}   & {100}   & {\%}                                & {}                                  & {\%}                                     & {}                                             & {\%}          & {}              & {\%}          & {}              \\
        \bottomrule
    \end{tabular}
    \caption{Results of the discriminators: $|V|$ are different vocabulary sizes, $h$ hidden sizes and $e$ embedding sizes.}
    \label{tab:results_discriminator}
\end{table}
\cmtDK{insert results of new experiments}

\begin{table}[h]
    \centering
    \begin{tabular}{c|ccccc|c}
        \hline
        \textbf{Dataset} & $h_{s}$ & $e_{s}$ & $h_{r}$ & $e_{r}$ & $|V|$ & \textbf{Acc.} \\
        \hline
        Dale-2           & {10}    & {10}    & {10}    & {10}    & {10}  & {95\%}        \\
        Dale-2           & {50}    & {50}    & {128}   & {128}   & {10}  & {50\%}        \\
        Dale-5           & {10}    & {10}    & {10}    & {10}    & {10}  & {23\%}        \\
        Dale-5           & {10}    & {10}    & {10}    & {10}    & {20}  & {23\%}        \\
        Dale-5           & {10}    & {10}    & {10}    & {10}    & {100} & {41\%}        \\
        \hline
    \end{tabular}
    \caption{Results: $h$ are different hidden sizes, $e$ embedding sizes and $|V|$ vocabulary sizes.}
    \label{tab:results}
\end{table}

@@

The results change, when using the \emph{Dale-5} dataset with four distractors.
With four distractors and with low hidden, embedding and vocabulary sizes, the agents barely pass the random baseline with 23\%.
Only increasing the vocabulary size to 100 raises the accuracy by almost 20\% points to 43\%.
This is still considerably lower than the 95\% of the \emph{Dale-2} dataset.

\cmtDK{calculation of loss?}

@@

\cmtDK{look at language}
\cmtDK{test different sizes}
\cmtDK{similarity to bounding box classifier}

@@

\begin{table}[h]
    \centering
    \begin{tabular}{cccc|ccc|ccc|ccc}
        \toprule
              &         &          &         & \multicolumn{3}{c}{\textbf{CLEVR single}} & \multicolumn{3}{c}{\textbf{Dale-2}} & \multicolumn{3}{c}{\textbf{Dale-5}}                                                                                                       \\\cmidrule(lr){5-7}\cmidrule(lr){8-10}\cmidrule(lr){11-13}
        $|V|$ & $h_{s}$ & $h_{r}$  & $e_{s}$ & \textbf{Dist.}                            & \textbf{Acc.}                       & \textbf{length}                     & \textbf{Dist.} & \textbf{Acc.} & \textbf{length} & \textbf{Dist.} & \textbf{Acc.} & \textbf{length} \\\midrule
        {10}  & {10}    & {10}     & {1024}  & {19,8}                                    & {55,1\%}                            & {2}                                 & {34,8}         & {24,3\%}      & {1}             & {44,3}         & {11,8\%}      & {2}             \\
        {10}  & {10}    & {10}     & {512}   & {9,3}                                     & {92\%}                              & {2}                                 & {36,3}         & {19,9\%}      & {1
        ,7}   & {45,9}  & {12,7\%} & {2}                                                                                                                                                                                                                                   \\
        {13}  & {10}    & {10}     & {1024}  & {7,8}                                     & {96,8\%}                            & {2}                                 & {36,3}         & {20,2\%}      & {1}             & {45,4}         & {11,4\%}      & {2}             \\
        {20}  & {10}    & {10}     & {1024}  & {6,6}                                     & {98,3\%}                            & {2}                                 & {37,8}         & {16,1\%}      & {2}             & {45,2}         & {11\%}        & {2}             \\
        {100} & {10}    & {10}     & {1024}  & {5,2}                                     & {98,5\%}                            & {2}                                 & {37,4}         & {20,1\%}      & {2}             & {43,6}         & {16,7\%}      & {2}             \\
        {100} & {100}   & {100}    & {1024}  & {12,5}                                    & {92,1\%}                            & {2}                                 & {36,5}         & {20,7\%}      & {2}             & {44,6}         & {12,7\%}      & {2}             \\
        \bottomrule
    \end{tabular}
    \caption{Results of the masked coordinate predictor: $|V|$ are different vocabulary sizes, $h$ hidden sizes and $e$ embedding sizes.}
    \label{tab:results_masked_predictor_game}

    Finally looking at the
\end{table}

>>>>

When the target object \textbf{attributes are encoded as one-hot vectors} and added to the input, the results don't improve.
One factor that now has a much higher impact is the feature extractor that is used.
Table \ref{tab:feature-extractor-mean-distances} compares the mean distances the models predict for the different feature extractors.
The results are shown for the models trained on the Dale-2 and Dale-5 datasets for training and test data.
First, a big difference can be seen between the datasets.
The model only converge to a minimum mean distance of around 46 pixels to the correct coordinates for the Dale-5 dataset, looking at the test data.
In most cases, it stays above 50 pixels.
Using the Dale-2 dataset, the behavior is a little different.
All ResNet extractors with four residual blocks and an additional average pooling and optionally a classifier layers reach similar scores as the experiments before without any one-hot encodings.
Interestingly, without the classifier layer, the model doesn't converge at all and the mean distances jump up and down between the epochs.
This effect also applies when using less residual blocks.
Using the VGG, only VGG-cls2 achieve a similar performance, while the others predict coordinates between 43 and 46 pixels away.

\begin{table}[h]
    \centering
    \begin{tabular}{rcccc}
        \toprule
                            & \multicolumn{2}{c}{\textbf{Dale-2}} & \multicolumn{2}{c}{\textbf{Dale-5}}                                   \\\cmidrule(lr){2-3}\cmidrule(lr){4-5}
                            & train                               & test                                & train          & test           \\\midrule
        \textbf{VGG-0}      & 30,27                               & 46,20                               & \textbf{32,17} & 54,40          \\
        \textbf{VGG-avg}    & \textbf{29,99}                      & 45,08                               & 32,32          & 52,67          \\
        \textbf{VGG-cls1}   & 37,99                               & 43,28                               & 46,57          & 50,75          \\
        \textbf{VGG-cls2}   & 38,87                               & \textbf{39,02}                      & 47,48          & 49,91          \\
        \textbf{VGG-cls3}   & 39,99                               & 44,32                               & 47,26          & \textbf{46,77} \\\midrule
        \textbf{ResNet-3}   & 78,26                               & 65,23                               & 92,07          & 91,12          \\
        \textbf{ResNet-4}   & 44,14                               & 55,24                               & \textbf{36,48} & 58,28          \\
        \textbf{ResNet-avg} & \textbf{33,06}                      & \textbf{39,18}                      & 47,64          & 46,38          \\
        \textbf{ResNet-cls} & 37,57                               & 38,10                               & 44,72          & \textbf{45,92} \\
        \bottomrule
    \end{tabular}
    \caption{Mean test losses for different feature extractors with one-hot attribute encodings after 20 epochs}
    \label{tab:feature-extractor-mean-distances}
\end{table}

Secondly, the training loss now looks also different.
In almost no cases, the models converge to a lower mean distance than with the test data, meaning a higher precision in their predictions, as they did in the experiment before.
The only exception is ResNet-3 as a feature extractor.
In other words, the models are again not able to generalize, but in specific cases memorize the patterns in the train data.
This hints to the fact that only specific layers of the feature extractors contain information that is generally usable to identify and discriminate objects.
Especially the lower layers with fewer residual blocks in the case of ResNet and no classifier layers for the VGG seem to not encode knowledge that can be utilized for this task.
Higher layers, with more specific encoded information need to be used for this research.
The experiments in the following sections are set up using these higher layers.

@@

In a next step, information about the attributes is included using the \textbf{\emph{GRE-algorithm}} from \citet{Dale1995}.
Again, the mean distance of the predictions as well as the accuracy doesn't improve compared to the previous experiments.

@@

These results allow two conclusions.
First, the models are biased to predict coordinates in the center of the image.
The reason for this is likely that the model can produce a relatively low loss, without relying on many extracted features of the objects.
Since all objects are always located in the center of the image and never in its corners, a prediction of any coordinate in the center is on average closer to the target object than any random prediction or predictions of coordinates at the borders of the image.
The model therefore learns only, where any object is likely located and can minimize the mean distance to a certain extent with this strategy.

Second, even though the models are biased towards the center of the image, the predictions are still often leaning towards the location where many objects lie.
This can be seen for the 'Dale-5' dataset, especially in left and central image in Figure \ref{fig:visualizations_dale-5_test}.
Again, by this strategy, the model can minimize the mean distance, since the probability is high that the target object lies in this cluster of objects.
Concluding, the model is able to extract, where objects are located in the image, but can't decide, which of these objects is the target object.

@@

Table \ref{tab:results_discriminator} shows the accuracy of the models calculated on the success of communication if the receiver can identify the target object.
A random guess corresponds to 50\% in the \emph{Dale-2} dataset and 20\% in the \emph{Dale-5} dataset.
Four different vocabulary sizes $|V|$ are tested.
A size of 13 symbols corresponds to the 13 attributes the objects can have and align with human language.
If the symbols were similarly used, messages would have lengths between one and three symbols.
Opposed to that a slightly smaller vocabulary with 10 symbols is used to create a smaller bottleneck with a higher pressure to condense the information.
Similarly, a bigger vocabulary consisting of 20 symbols tests how a bigger bottleneck changes the results.
Lastly, a big vocabulary of 100 symbols should give the model all options to encode the information, including one symbol per attribute or one symbol describing a combination of attributes.

The hidden sizes $h_s$ and $h_r$ as well as the embedding sizes $e_s$ and $e_r$ are chosen in alignment with the vocabulary size.
The hidden sizes are always smaller or equal to the vocabulary size since the information about each word needs to be compressed in a smaller dimension to learn meaning.
Hereby, hidden sizes of 10 and 100 are tested.
On the other hand, three different embedding sizes are tested: 10, 50 and 100.
The reason for this is to experiment, what is the optimal middle ground between compressing features of an image encoded in high dimension vectors and upscaling encoded messages in low dimension vectors.

\begin{table}[h]
    \centering
    \begin{tabular}{ccccc|cc|cc|cc}
        \toprule
              &         &         &         &         & \multicolumn{2}{c}{\textbf{Dale-2}} & \multicolumn{2}{c}{\textbf{Dale-5}} & \multicolumn{2}{c}{\textbf{CLEVR color}}                                                         \\\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-11}
        $|V|$ & $h_{s}$ & $h_{r}$ & $e_{s}$ & $e_{r}$ & \textbf{Accuracy}                   & \textbf{length}                     & \textbf{Accuracy}                        & \textbf{length} & \textbf{Accuracy} & \textbf{length} \\\midrule
        {10}  & {10}    & {10}    & {10}    & {10}    & {96,4\%}                            & {1,99}                              & {24,7\%}                                 & {1}             & {17,3\%}          & {2}             \\
        {10}  & {50}    & {50}    & {50}    & {50}    & {50\%}                              & {2}                                 & {21,4\%}                                 & {2}             & {17,8\%}          & {1}             \\
        {13}  & {10}    & {10}    & {10}    & {10}    & {94,9\%}                            & {2}                                 & {24,8\%}                                 & {2}             & {17,1\%}          & {2}             \\
        {13}  & {10}    & {10}    & {50}    & {50}    & {49,6\%}                            & {2}                                 & {21,9\%}                                 & {2}             & {17,9\%}          & {1}             \\
        {20}  & {10}    & {10}    & {50}    & {50}    & {50,9\%}                            & {1}                                 & {23\%}                                   & {2}             & {15,9\%}          & {2}             \\
        {100} & {10}    & {10}    & {10}    & {10}    & {97,3\%}                            & {2}                                 & {24\%}                                   & {2}             & {18,1\%}          & {2}             \\
        {100} & {10}    & {10}    & {50}    & {50}    & {49,9\%}                            & {2}                                 & {24,4\%}                                 & {2}             & {15,8\%}          & {2}             \\
        {100} & {100}   & {100}   & {100}   & {100}   & {49\%}                              & {1}                                 & {25,3\%}                                 & {2}             & {15,6\%}          & {1}             \\
        \bottomrule
    \end{tabular}
    \caption{Results of the discriminators: $|V|$ are different vocabulary sizes, $h$ hidden sizes and $e$ embedding sizes.}
    \label{tab:results_discriminator}
\end{table}

@@

The results change, when using the \emph{Dale-5} dataset with four distractors.
With four distractors and with low hidden, embedding and vocabulary sizes, the agents barely pass the random baseline with 23\%.
Only increasing the vocabulary size to 100 raises the accuracy by almost 20\% points to 43\%.
This is still considerably lower than the 95\% of the \emph{Dale-2} dataset.
The same applies to the 'CLEVR color' dataset, where all models achieve a very low accuracy of around 15 to 17\%, corresponding to random guesses.

\cmtDK{calculation of loss?}
\cmtDK{length}

@@

\cmtDK{look at language}
\cmtDK{similarity to bounding box classifier}

@@

\begin{table}[h]
    \centering
    \begin{tabular}{cccc|ccc|ccc|ccc}
        \toprule
              &         &          &         & \multicolumn{3}{c}{\textbf{CLEVR single}} & \multicolumn{3}{c}{\textbf{Dale-2}} & \multicolumn{3}{c}{\textbf{Dale-5}}                                                                                                       \\\cmidrule(lr){5-7}\cmidrule(lr){8-10}\cmidrule(lr){11-13}
        $|V|$ & $h_{s}$ & $h_{r}$  & $e_{s}$ & \textbf{Dist.}                            & \textbf{Acc.}                       & \textbf{length}                     & \textbf{Dist.} & \textbf{Acc.} & \textbf{length} & \textbf{Dist.} & \textbf{Acc.} & \textbf{length} \\\midrule
        {10}  & {10}    & {10}     & {1024}  & {19,8}                                    & {55,1\%}                            & {2}                                 & {34,8}         & {24,3\%}      & {1}             & {44,3}         & {11,8\%}      & {2}             \\
        {10}  & {10}    & {10}     & {512}   & {9,3}                                     & {92\%}                              & {2}                                 & {36,3}         & {19,9\%}      & {1
        ,7}   & {45,9}  & {12,7\%} & {2}                                                                                                                                                                                                                                   \\
        {13}  & {10}    & {10}     & {1024}  & {7,8}                                     & {96,8\%}                            & {2}                                 & {36,3}         & {20,2\%}      & {1}             & {45,4}         & {11,4\%}      & {2}             \\
        {20}  & {10}    & {10}     & {1024}  & {6,6}                                     & {98,3\%}                            & {2}                                 & {37,8}         & {16,1\%}      & {2}             & {45,2}         & {11\%}        & {2}             \\
        {100} & {10}    & {10}     & {1024}  & {5,2}                                     & {98,5\%}                            & {2}                                 & {37,4}         & {20,1\%}      & {2}             & {43,6}         & {16,7\%}      & {2}             \\
        {100} & {100}   & {100}    & {1024}  & {12,5}                                    & {92,1\%}                            & {2}                                 & {36,5}         & {20,7\%}      & {2}             & {44,6}         & {12,7\%}      & {2}             \\
        \bottomrule
    \end{tabular}
    \caption{Results of the masked coordinate predictor: $|V|$ are different vocabulary sizes, $h$ hidden sizes and $e$ embedding sizes.}
    \label{tab:results_masked_predictor_game}
\end{table}

Finally looking at the
